Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-16 talk/iwtc11/paper.tex
a minimal introduction section on PyPy

\title{Loop Invariant Code Motion in PyPy's Tracing JIT}
%\subtitle{Subtitle Text, if any}

@@

>>>>

\title{Loop-Aware Optimizations in PyPy's Tracing JIT}
%\subtitle{Subtitle Text, if any}

@@

\section{Background: PyPy}
\label{sec:PyPy}

The work described in this paper was done in the context of the PyPy
project\footnote{\url{http://pypy.org}}. PyPy is a framework for implementing
dynamic languages efficiently \cite{armin_rigo_pypys_2006}. When implementing a
language with PyPy, one writes an interpreter for the language in RPython
\cite{davide_ancona_rpython:_2007}. RPython (``Restricted Python``) is a subset
of Python chosen in such a way that it can be efficiently translated to a
C-based VM by performing type inference.

Many low-level aspects of the final VM are not contained within the interpreter
implementation but are inserted during translation to C. Examples for this are a
garbage collector and also a tracing JIT compiler \cite{bolz_tracing_2009}.

PyPy's tracing JIT compiler traces on the level of RPython programs. Thus it
actually traces the execution of an interpreter written in RPython, not of the
program itself. This makes the details of the object model of the implemented
language transparent and optimizable by the tracing JIT. In the context of this
paper, this aspect of PyPy's tracing JIT can be ignored. Instead, it is
sufficient to view PyPy's tracing JIT as a JIT for RPython.

% section PyPy (end)
